\documentclass[12pt]{article}
\usepackage{amsmath,amsfonts}
\usepackage[cm]{fullpage}
\usepackage{fancyvrb}

\title{Senior Test 4}
\author{Stellenbosch Camp 2017}
\date{Time: $2\frac{1}{2}$ hours}


\begin{document} \maketitle

\begin{enumerate}

\item[1.] % Croatian 2nd Round, county competition, 2017
Does there exist a positive integer $m$ such that $2^{m^2} - 4$ is divisible by $7$?


\item[2.] % AoPS GovernmentCheeseAhoy
There are $2017^2$ desks arranged in $2017 \times 2017$ square. Is there a permutation of the desks that leaves each desk in an adjacent position (up, down, right or left) with respect to its original position?


\item[3.] % Catspiration
Let $\Gamma$ be a circle with two chords $AB$ and $CD$ which intersect at point $X$ inside $\Gamma$. Let $M$ and $N$ be the midpoints of $AB$ and $CD$ respectively. Show that if $MN$ is parallel to the angle bisector of $\angle AXC$, then $AB = CD$.


\item[4.] % Tim Drake
A positive integer $n$ is called \emph{interesting} if there exists a function $f : \mathbb{R} \to \mathbb{R}$ such that
  \[ f(x) - f(x+y) = y^n \quad \forall x,y \in \mathbb{R}. \]
A positive integer $n$ is called \emph{beautiful} if there exists a function $f : \mathbb{R} \to\mathbb{R}$ such that
  \[ f(x) - f(x+y) \leq y^n \quad \forall x,y \in \mathbb{R}. \]
Find all interesting positive integers and all beautiful positive integers.
 

\item[5.] % https://math.stackexchange.com/questions/581461/what-is-the-minimum-number-of-locks-on-the-cabinet-that-would-satisfy-these-cond
Eleven scientists want to have a cabinet built where they will keep some top secret work. They want multiple locks installed, with keys distributed in such a way that if any six scientists are present then they can open all the locks, but if only five are present then they cannot open all the locks. Each key can open exactly one lock. What is the minimum number of locks on the cabinet that would satisfy these conditions?


\end{enumerate}

\vfill

\centering
\begin{BVerbatim}
      ,/|         _.--''^``-...___.._.,;
     /, \'.     _-'          ,--,,,--'''
    { \    `_-''       '    /}
     `;;'            ;   ; ;
 ._.--''     ._,,, _..'  .;.'
  (,_....----'''     (,..--''
\end{BVerbatim}

\end{document}

