\documentclass[12pt]{article}
\usepackage{amsmath,amsfonts}
\usepackage[cm]{fullpage}

\pagenumbering{gobble}

\title{\vspace{-12pt}March Monthly Problem Set}
\author{Due: 12 March 2018}
\date{}


\begin{document} \maketitle \pagestyle{empty}

\begin{enumerate}

\item % Easy, Dutch BxMO Selection Test 2016
For a positive integer that is not a power of 2, define $t(n)$ as the greatest odd divisor of $n$ and $r(n)$ as the smallest odd divisor of $n$ greater than 1. Determine all positive integers $n$ which are not powers of 2 and satisfy
	\[ n = 3t(n)+5r(n).\]


\item % PP-2005-3
$ABCD$ is a square. At $B$, another square $BEFG$ is drawn so that $\angle ABE$ is obtuse. Prove that the median through $B$ of triangle $BCG$ is perpendicular to $AE$.


\item % PP-2006-3
A hexagon is partitioned into triangles, each coloured either black or white, such that:
\begin{enumerate}
\item Two triangles either share a common side (and then they are of different colours) or a common vertex, or else they have no points in common.
\item Every side of the hexagon is also a side of one of the black triangles.
\end{enumerate}
Prove that a decagon cannot be partitioned in this way.


\item % SW-2013-4
Determine all pairs of functions $(f,g)$ from the set of real numbers to itself such that
\[ \min(f(x),f(y)) = \max(g(x),g(y)) \]
for all real numbers $x$ and $y$ with $x \neq y$.


\item % Argentine National Olympiad 2016 1st Level Q2 -- C, Q4
Given 100 infinitely large boxes with finitely many markers in each of them, the following procedure is carried out: At step 1 one adds one marker in every box. At step 2 one marker is added in every box containing an even number of markers. At step 3 one marker is added in every box in which the number of markers is divisible by 3, and so on. Before the process starts Bruno wants to distribute several markers in the boxes such that there is at least one marker in each box and the following holds: after any number of steps there exist two boxes containing a different number of markers. Is it possible for Bruno to do this?


\item % SW-2009-6
Let $n > 1$ be an integer. Prove that the inequality
\[ \frac{(n-1)^2}{4} \geq \left(\sum_{1 \leq i < j \leq n} \sqrt{x_i x_j}\right)^2 + \left(\sum_{1 \leq i < j \leq n} \left\lvert x_i-x_j \right\rvert \right)^2 \]
holds for all nonnegative real numbers $x_1, x_2, \dotsc, x_n$ with $x_1 +x_2 +\dotsb +x_n = 1$.


\item % Hard (Med-Hard?) Dutch BxMO Selection Test 2016
$\triangle ABC$ is right-angled with $\angle A=90^\circ$ and circumcircle $\Gamma$. The incircle of $\triangle ABC$ touches $BC$ at $D$, $CA$ at $E$ and $AB$ at $F$. Let $M$ be the midpoint of arc $AB$ of $\Gamma$ not containing $C$ and let $N$ be the midpoint of arc $AC$ of $\Gamma$ not containing $B$. Prove that $E$, $F$, $M$ and $N$ lie on a straight line.


\item % JM-2007-4
Let $m,n$ be positive integers and $p > 3$ a prime number such that $\gcd(m,p-1) = \gcd(n,p-1) = 1$, and assume that $(a^m + b^m)^n \equiv (a^n + b^n)^m \pmod{p}$ for all integers $a$ and $b$.

Prove that $m \equiv n \pmod{p-1}$.


\end{enumerate}

\end{document}
