\documentclass[12pt]{article}
\usepackage{amsmath,amsfonts}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{enumitem}

\pagenumbering{gobble}

\title{May Monthly Problem Set}
\author{Due: 31 May 2018}
\date{}


\begin{document} \vspace{-12pt} \maketitle \pagestyle{empty}

\begin{enumerate}

\item % Taiwan TST 2014 TST Round 1 Mock IMO Q2
For a fixed integer $k$, determine all polynomials $f(x)$ with integer coefficients such that $f(n)$ divides $(n!)^k$ for every positive integer $n$.

\item % IMO Shortlist 2013 C6
In some country several pairs of cities are connected by direct two-way flights. It is possible to go from any city to any other by a sequence of flights. The distance between two cities is defined to be the least possible numbers of flights required to go from one of them to the other. It is known that for any city there are at most $100$ cities at distance exactly three from it. Prove that there is no city such that more than $2550$ other cities have distance exactly four from it.

\item % IMO Shortlist 2014 G4
Consider a fixed circle $\Gamma$ with three fixed points $A, B,$ and $C$ on it. Also, let us fix a real number $\lambda \in(0,1)$. For a variable point $P \not\in\{A, B, C\}$ on $\Gamma$, let $M$ be the point on the segment $CP$ such that $CM =\lambda\cdot  CP$ . Let $Q$ be the second point of intersection of the circumcircles of the triangles $AMP$ and $BMC$. Prove that as $P$ varies, the point $Q$ lies on a fixed circle.

\item % IMO Shortlist 2013 A5
Let $\mathbb{Z}_{\ge 0}$ be the set of all nonnegative integers. Find all the functions $f: \mathbb{Z}_{\ge 0} \rightarrow \mathbb{Z}_{\ge 0} $ satisfying the relation
\[ f(f(f(n))) = f(n+1 ) +1 \]
for all $ n\in \mathbb{Z}_{\ge 0}$.

\end{enumerate}


\small
\subsection*{Email submission guidelines}

\begin{itemize}
\item Submit each question in a single separate PDF file (with multiple pages if necessary), with your name and the question number written on each page.
\item If you take photographs of your work, use a document scanner such as \verb!CamScanner! to convert to PDF.
\item If you have multiple PDF files for a question, combine them using software such as \verb!PDFsam!.
\end{itemize}

\end{document}
