\documentclass[12pt]{article}
\usepackage{amsmath,amsfonts}
\usepackage[cm]{fullpage}
\usepackage{fancyvrb}

\title{Monthlies Pool}
\author{Stellenbosch Camp 2017}


\begin{document} \maketitle

\begin{itemize}

\item % Scry 2, Magic the Gathering

Consider a deck of $n$ cards with cards numbered from $1$ to $n$. There is one card of each number, but the deck is shuffled, so the cards do not necessarily appear in numerical order. You are allowed to perform the following operation on the deck: You look at the top two cards of the deck, and place one of these two cards on the bottom of the deck, and the other card on top. Show that it possible, using only this operation some number of times, to sort the deck so that the cards appear in ascending order. 


\item % Argentine National Olympiad 2016 1st Level Q2 -- C, Q4
Given 100 infinitely large boxes with finitely many markers in each of them, the following procedure is carried out: At step 1 one adds one marker in every box. At step 2 one marker is added in every box containing an even number of markers. At step 3 one marker is added in every box in which the number of markers is divisible by 3, and so on. Before the process starts Bruno wants to distribute several markers in the boxes such that there is at least one marker in each box and the following holds: after any number of steps there exist two boxes containing a different number of markers. Is it possible for Bruno to do this?


\item % Hellenic Math Olympiad 2017 Juniors Q3
Determine all positive integers $a,b,p$, where $p$ is prime, satisfying the following equation:
  \[ \frac{1}{p} = \frac{1}{a^2} + \frac{1}{b^2}. \]


\item % Med-Hard, Dutch BxMO Selection Test 2016
Determine all pairs of positive integers $(m,n)$ for which
	\[(m+n)^3 \mid 2n(3m^2+n^2) + 8.\]


\item % Easy, Dutch BxMO Selection Test 2016
For a positive integer that is not a power of 2, define $t(n)$ as the greatest odd divisor of $n$ and $r(n)$ as the smallest odd divisor of $n$ greater than 1. Determine all positive integers $n$ which are not a power of 2 and satisfies
	\[ n = 3t(n)+5r(n).\]


\item % Med-Hard? Dutch IMO Selection 2016
Let $k$ be a positive integer, and let $s(n)$ denote the sum of the digits of $n$. Show that among all positive integers with $k$ digits, there are as many numbers $n$ satisfying $s(n)<s(2n)$ as there are numbers $n$ satisfying $s(n)>s(2n)$.


\item % Med? Germany 2015
For a certain value of $n$, the numbers $4^n$ and $5^n$ start with the same digit. Prove that this digit must be either a 2 or a 4.


\item % Hard Dutch IMO Selection 2016
Let $\Gamma_1$ be a circle with centre $A$ and $\Gamma_2$ be a circle with centre $B$ such that $A$ lies on $\Gamma_2$. On $\Gamma_2$ there is a (variable) point $P$ not lying on $AB$. A line through $P$ is a tangent of $\Gamma_1$ at $S$, and it intersects $\Gamma_2$ again in $Q$, with $Q$ and $P$ lying on the same side of $AB$. A different line through $Q$ is tangent to $\Gamma_1$ at $T$. Moreover, let $M$ be the foot of the perpendicular to $AB$ through $P$. Let $N$ be the intersection of $AQ$ and $MN$. 
	
Prove that $N$ lies on a line independent of the positive of $P$ on $\Gamma_2$.


\item % Hard (Med-Hard?) Dutch BxMO Selection Test 2016
$\triangle ABC$ is right-angled with $\angle A=90^\circ$ and circumcircle $\Gamma$. The incircle of $\triangle ABC$ touches $BC$ at $D$, $CA$ at $E$ and $AB$ at $F$. Let $M$ be the midpoint of arc $AB$ of $\Gamma$ not containing $C$ and let $N$ be the midpoint of arc $AC$ of $\Gamma$ not containing $B$. Prove that $E$, $F$, $M$ and $N$ lie on a straight line.


\item % Easy-Med? Germany 2015
Let $M$ be the midpoint of side $AB$ of $\triangle ABC$ in which $BC>CA$. The perpendicular bisector of $AB$ meets $BC$ in $P$ and $AC$ extended in $Q$. Let $R$ be the foot of the perpendicular from $P$ onto $AC$ and let $S$ be the foot of the perpendicular from $Q$ onto $BC$. Prove that $M$, $R$ and $S$ lie on a straight line.


\item % Hard? Dutch IMO Selection 2016
Determine the number of sets $A=\{a_1,a_2,\ldots, a_{1000}\}$ of positive integers satisfying $a_1<a_2<\cdots a_{1000}\le 2014$ for which the set
	\[ S = \{a_i+a_j\mid 1\le i,j\le 1000,\ i+j\in A\} \]
is a subset of $A$.

\item % Med? Belarus Selection 2017
Given positive real $a,b,c$ such that $2abc+ab+bc+ca=1$, prove the inequality
\begin{equation*}
\frac{a+1}{(a+1)^2+(b+1)^2}+\frac{b+1}{(b+1)^2+(c+1)^2}+\frac{c+1}{(c+1)^2+(a+1)^2}\leq 1
\end{equation*}.

\item % Easy-Med? Belarus Selection 2017
Find all prime numbers $a$ and $b$ such that
\begin{equation*}
20a^3-b^3=1
\end{equation*}


\end{itemize}

\vfill

\centering
\begin{BVerbatim}
\end{BVerbatim}

\end{document}
